### 2016-11-30 local-capability-machine.tex
Public monotonicity of memory satisfaction does not hold (please read comment)

ML-like program:
\begin{verbatim}
let f = fun adv =>
          let l = 1 in
          adv(l);
          l := 1;
          adv(0);
          assert(!l == 1)
\end{verbatim}
In this example \texttt{let l = 1 in} allocates a new local capability \texttt{l} with read-write permissions. Assuming \texttt{adv} has no access to capabilities with permit write local, they cannot store \texttt{l} and thus change its value in the second call.

@@

@@

\begin{lemma}[Public monotonicity]
  \begin{align*}
    & \forall \hs, n, W' \futurewk W \ldotp \\
    & \quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n}{W'}
  \end{align*}
\end{lemma}

>>>>

\lau{I have skipped the following program in favor of the one in the next section. }
ML-like program:
\begin{verbatim}
let f = fun adv =>
          let l = 1 in
          adv(l);
          l := 1;
          adv(0);
          assert(!l == 1)
\end{verbatim}
In this example \texttt{let l = 1 in} allocates a new local capability \texttt{l} with read-write permissions. Assuming \texttt{adv} has no access to capabilities with permit write local, they cannot store \texttt{l} and thus change its value in the second call.

@@

\begin{verbatim}
f3: push 1
    scall adv([],[])
    pop r1
    assert r1 1
    push 2
    scall adv([],[])
3f: halt
\end{verbatim}

@@

\begin{lemma}[Public monotonicity]
\lau{This is not true! If the new region is active and does not accept the empty memory, then it is no longer possible to make a satisfactory partition of the heap.}
  \begin{align*}
    & \forall \hs, n, W' \futurewk W \ldotp \\
    & \quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n}{W'}
  \end{align*}
\end{lemma}
